Scalar_M1

### 2015-05-16 models/Model_Playspace.Rmd
more alternatives'
minor tweaks to model formatting

  if (useprior) {
    prior <- priors[rating, "prior.p"]
  } else {
    prior = .2 
  }

@@

  if (usenone) {
    mat$none <- c(1, 0, 0, 0, 0)
  }

@@

```{r}
md <- data %>%
  do(run.rsa(., alpha = 1, useprior = FALSE, usenone = TRUE))

qplot(stars, listener.p, col=degree, 
      data = md) + 
  facet_wrap(~scale) + 
  geom_line(aes(y = pred), lty = 2)
```

>>>>

  if (useprior) {
    prior <- priors[rating, "prior.p"]
  } else { #unif prior
    prior = .2 
  }

@@

  if (usenone) {
    mat$none <- c(.8, .2, 0, 0, 0)
    mat$bad <- c(.25, .5, .25, 0, 0)

  }

@@

```{r}
md <- data %>%
  do(run.rsa(., alpha = 10, useprior = FALSE, usenone = TRUE))

qplot(stars, listener.p, col=degree, 
      data = md, main="Model vs Human judgments") + 
  facet_wrap(~scale) + 
  geom_line(aes(y = pred), lty = 2)
```
